Selecting and Controlling Physical Devices Through a Head-Mounted Display with Infrared Targeting

### 2013-09-02 doc/sigchi14/introduction.tex
tweaks

Our hardware relies on infrared communication between Glass and target devices to establish a connection; and on wireless ZigBee radio communication to exchange control messages.  Target devices similarly have IR receivers and ZigBee radios. These choices provide an orientation-specific  step selection appropriate for the limitations of head orientation; once acquired, users do not have to look at the target device for control commands.

>>>>

Our hardware relies on infrared communication between Glass and target devices to establish a connection; and on wireless ZigBee radio communication to exchange control messages.  Target devices similarly have IR receivers and ZigBee radios. These choices offer selection-through-head-orientation to initiate interaction; once initiated, users do not have to look at the target device for control commands.
